Exploring probability distributions for bivariate temporal granularities

### 2019-11-18 main.Rmd
synergy of time granularities

The levels (very high/high/medium/low) of the two granularities plotted might have an impact on the choice of plots. The criteria for different levels could be based on usual cognitive power while comparing across facets and display size available to us. Space and resolution become a problem if the number of levels of facet variables is too high. Hence, plot choices will also vary depending on which granularity is placed on the x-axis and which one across facets.

@@

@@

## Effect of synergy

@@

We should avoid plotting clashes as they hinder the exploratory process by having missing combinations of time granularities in each panel.

```{r allFig, fig.height=5.5, out.width="50%", fig.pos = "h", fig.align= 'left',echo=FALSE, eval=TRUE, warning=FALSE,message = FALSE, fig.cap="Various probability distribution plots of electricity consumption data of Victoria from 2012 to 2014. (a) Letter value plot by DoM and MoY, (b) Decile plot by HoD and DoW (c) Box plot by DoY and DoM, (d) Violin plot of DoM and WoM, (e) Ridge plot by WoM and WoY, (f) Decile plot by DoY and MoY. Only plots (a) and (b) show harmonised time variables.", fig.show = 'hold'}

>>>>

The levels of the two granularities plotted might have an impact on the choice of plots since space and resolution might become a problem if the number of levels are too high. The criteria for different levels could be based on usual cognitive power while comparing across facets and display size available to us. Plot choices will also vary depending on which granularity is placed on the x-axis and which one across facets.

@@

The following principles are useful while choosing distribution plots given two temporal granularities.

@@

## Effect of synergy
In Section \ref{sec:harmonyclash}, we discussed how pairs of granularities can have empty combinations either due to structure of calendar, event location or duration or due to the way they are build. In this section, we will see how these empty combinations affect the visualization when a dependent variable is plotted against these granularities.

@@

Hence we redefine harmony and clashes as follows : harmonies are pairs of granularities that aid exploratory data analysis, and clashes are pairs that are incompatible with each other for exploratory analysis. Hence, we should avoid plotting clashes as they hinder the exploratory process by having missing combinations of time granularities in each panel.

```{r allFig, fig.height=5.5, out.width="50%", fig.align= 'left',echo=FALSE, eval=TRUE, warning=FALSE,message = FALSE, fig.cap="Various probability distribution plots of electricity consumption data of Victoria from 2012 to 2014. (a) Letter value plot by DoM and MoY, (b) Decile plot by HoD and DoW (c) Box plot by DoY and DoM, (d) Violin plot of DoM and WoM, (e) Ridge plot by WoM and WoY, (f) Decile plot by DoY and MoY. Only plots (a) and (b) show harmonised time variables.", fig.show = 'hold'}
